\documentclass[]{article}

%opening
\title{Game Data Mining\\Project Outline}

\author{Luke Korpalski\\luk10@aber.ac.uk\\
	    GG4R: Computer Science And Artificial Intelligence\\
		CS39440\\
	  \\Richard Jenson\\rkj@aber.ac.uk\\}
  
\date{February 2020\\
      v1.0 Release}


\begin{document}

\maketitle

\newpage
\section{Project Description}
The Game Data Mining major project aims to extract useful information from a video-game dataset.
This is a research-centric project with some software deliverables developed to model the data.
Originally based on a competition to model a dataset of the MMORPG `\textit{Blade and Soul}', the project is now more open-ended due to the dataset no longer being available online.
\\

Research using game datasets typically seeks to model player behaviour to maximise profitability of the game \cite{kaw09}, to study human behaviour, or to test economic theory \cite{shen12}.
A study \cite{lee18} of game log data from the MMORPG `\textit{Lineage}' used social network analysis on in-game transactions (or \textit{trades}) between players.
The modelled data was then used to identify networks of black-market real-money trading (RMT).

This project proposes to use similar techniques to model economic data in other multiplayer games.
In-game market data is available for the MMO `\textit{EVE Online}' through an official web API \cite{ccp}.
This seems a good starting point for the project.

The models produced in this project will be visualised and evaluated, with comparison to related research.


\vspace{1cm}
\section{Proposed Tasks}
\begin{itemize}
	\item \textbf{Project diary}---a record of the project's on-going development.
	Done in the form of a blog using the personal webpage provided by Aberystwyth University.
	
	\item \textbf{Research reading}---further reading of relevant research will likely be required to effectively progress in the project.
	May also influence the project's direction and methods.
	
	\item \textbf{Refining use of Agile techniques}---as the Agile methodology is not best suited to a research solo project, effectiveness of its techniques should be evaluated.
	Useful aspects of Agile more suited to this project should be identified early on.
	
	\item \textbf{Modelling the data}---application of chosen data mining techniques to produce a model of the data.
	Probably using Python with relevant libraries.
	Includes the use of test sets to produce a measure of accuracy.
	
	\item \textbf{Production of report}---final write-up of the project for hand-in.
	Will include further discussion and conclusion of the used techniques and produced models.

\end{itemize}


\vspace{1cm}
\section{Project Deliverables}
\begin{itemize}
	\item \textbf{Datasets}---the datasets used in the project, after extracting the useful data.
	Will be produced at the start of the project, with potential modification to suit changing needs.
	
	\item \textbf{GitHub source control}---a GitHub \cite{gh} repository containing a backup of the project history.
	Mainly serving as a fail-safe to protect the work done.
	This should be set up at the start of the project and used throughout to track changes in the project deliverables.
	
	\item \textbf{Data models}---the software developed to represent the data, and its output.
	Will be started following acquirement of a suitable dataset, with ideally at least one good model produced before the mid-project demonstration.
	
	\item \textbf{Data visualisation}---graphical representation of the models and/or initial data.
	Acts as a visual aid in the final report.
	Can be started once a data model has been made, ideally with one being produced for the mid-project demonstration.
	
	\item \textbf{Final report}---the document compiling all work done with additional discussion.
	This will be the last work to be completed.

\end{itemize}

\vspace{1cm}
\begin{thebibliography}{9}
	\bibitem{kaw09}
	J. Kawale, A. Pal and J. Srivastava,
	``Churn Prediction in MMORPGs: A Social Influence Based Approach,'' 2009 International Conference on Computational Science and Engineering,
	Vancouver, BC,
	2009,
	pp. 423-428.
	
	\bibitem{shen12}
	C. Shen, P. Monge, and D. Williams,
	``Virtual Brokerage and Closure: Network Structure and Social Capital in a Massively Multiplayer Online Game''
	Communication Research, vol. 41, no. 4,
	2014,
	pp. 459–480, 
	doi:10.1177/0093650212455197.
	
	\bibitem{lee18}
	E. Lee, J. Woo, H. S. Kim, and H. K. Kim,
	``No Silk Road for Online Gamers!: Using Social Network Analysis to Unveil Black Markets in Online Games,''
	Proc. 2018 World Wide Web Conf.,
	2018,
	pp. 1825-1834.
	
	\bibitem{ccp}
	CCP Games,
	\textit{EVE Swagger Interface},
	[Online],
	Available: https://esi.evetech.net.
	[Accessed Feb. 13 2020]
	
	\bibitem{gh}
	GitHub, Inc,
	\textit{GitHub}.
	[Online],
	Available: https://github.com.
	[Accessed Feb. 13 2020].
	
\end{thebibliography}

\end{document}
